Formalization of Abstract Rewriting

### 2025-02-12 Relations/Paper/Definitions.tex
updates...

We denote a relation $R$ (from the set $R_\alpha$) from an element $a \in A$ to an element $b \in A$ as $a\rstep b$.
A multi-step relation is denoted $a \mstep b$.

\begin{definition}
    An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
    via multi-step relations to some common reduct.

@@

\begin{definition}
    \emph An element $a \in A$ is a {normal form} if there exists no relation to any other element in $A$.
\end{definition}

>>>>

For the rest of this section, let $A$ be a fixed set, and $R$ be a relation on $A$.
(In the Agda code supplement, this is represented by a type $A : \bset$,
and a binary type family $R : A \to A \to \bset$.)

\greyout{We denote by $\tilde R$ the relational converse of $R$ ($(x,y) \in \tilde R \iff (y,x) \in R$),
and by $R;R'$ the relational composition of $R$ and $R'$.}

\begin{notation}
  The following notions are standard.  For precise definitions,
  see \texttt{ClosureOperators.agda}.
  \begin{enumerate}
    \item $R^r$ denotes the \emph{reflexive closure} of $R$.
    \item $R^s$ denotes the \emph{symmetric closure} of $R$.
    \item $R^+$ denotes the \emph{transitive closure} of $R$.
    \item $R^* = (R^r)^+$ denotes the \emph{reflexive-transitive closure} of $R$.
    \item $R^= = (R^s)^*$ denotes the \emph{equivalence relation generated by} $R$.
  \end{enumerate}
\end{notation}

In the context of abstract rewriting, we will often write $a \rstep_R b$
in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
$a \bstep b$ for $(b,a) \in R$.  When the relation $R$ is clear from the context,
we may drop the corresponding subscript.

We first define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.

\begin{definition}  Let $A$ and $R$ be as above, and let $a \in A$.
  \begin{description}
    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[$a \in SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
  \end{description}

    An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
    via multi-step relations to some common reduct.

@@

\begin{definition}
  \label{d:WFacc}
  An element is \emph{accessible} if ...
\end{definition}
